---
title: "p8105_hw1_tw3128"
author: "Chris"
date: "2025-09-14"
output: github_document
---

# Problem 1

## Load the Package and Dataset
First, I load the package.

```{r}
library(moderndive)
library(tidyverse)
```


Second, I load the dataset "early_january_weather" from the package.

```{r loading_the_data}
data("early_january_weather")
```


## Discription

```{r show introductions to myself, include = FALSE}
names(early_january_weather)
?early_january_weather
```

* The dataset "early_january_weather" shows the Hourly meteorological data for LGA, JFK and EWR for the month of January 2013, which contains `r ncol(early_january_weather)` variables. These variables are `r names(early_january_weather)`. Here are some brief descriptions below.


  * Variable "origin" means the weather station where it locates. 

  * Variables "year", "month", "day" and "hour" are the time of recording. 

  * "temp" and "dewp" are temperature and dewpoint in Fahrenheit. 

  * "humid" means the relative humidity. "wind_air", "wind_speed" and "wind_gust" refer to wind direction, speed and gust speed respectively.

  * "precip" means the precipitation in inches.

  * "pressure" means sea level pressure in millibars.

  * "visib" means visibility in miles.

  * "time_hour" means date and hour of the recording as a POSIXct date.


* There are `r nrow(early_january_weather)` samples and `r ncol(early_january_weather)` variables.


* The mean temperature is `r mean(early_january_weather$temp)`.


## Scatterplot

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +           geom_point() + 
  labs(
    x = "Time (hour)",
    y = "Temperature (\u00B0F)",
    color = "Humidity",
    title = "Temperature-Time with Humidity"
  ) +
  theme_minimal()

ggsave("temp-time-scatterplot_from-problem01.png")
```
























